Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-06-07 Master Thesis/synopsis.tex
Refactor

Let $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$ and $w\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ with $v(w)=v$. Then $k(v)$ is finitely generated of dimension $1$ by Lemma \ref{rank-dimension-inequality}, thus a global field. By Theorem \ref{theorem-absoluteinertia}, we have: 
\[G_{K_w}/H \cong \operatorname{Gal}(K_v^\text{t}/K_w)\cong G_{k(v_w)}\] 
where $v_w$ is the unique extension of $v$ on $K_w$ and $H=G_{K_v^\text{t}}$. With Lemma \ref{2.2-pre} we can see that $k(v_w)$ is the henselization of $k(v)$ with respect to $w\mod v\in\operatorname{Spv}k(v)$. Let $N$ be the closed subgroup of $G_{K_v}$ generated by all subgroups $G_{K_w}$ for $w\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ with $v(w) = v$. Since a global field has no non-trivial algebraic extension in which every prime splits completely, we get $N/H= G_{K_v}/H\cong G_{k(v)}$, thus $N=G_{K_v}$. Since $(K_w)'=K'_{w'}$, this shows that $(K_v)'$ is a henselization of $K'$ with respect to $v'=\sigma(v)$. We write $K'_{v'} = (K_v)'$.

>>>>

Let $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$ and $w\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ with $v(w)=v$. Then $k(v)$ is finitely generated of dimension $1$ by Lemma \ref{rank-dimension-inequality}, thus a global field. By Theorem \ref{theorem-absoluteinertia}, we have: 
\[G_{K_w}/N \cong \operatorname{Gal}(K_v^\text{t}/K_w)\cong G_{k(v_w)}\] 
where $v_w$ is the unique extension of $v$ on $K_w$ and $N=G_{K_v^\text{t}}$. With Lemma \ref{2.2-pre} we can see that $k(v_w)$ is the henselization of $k(v)$ with respect to $w\mod v\in\operatorname{Spv}k(v)$. Let $H$ be the closed subgroup of $G_{K_v}$ generated by all subgroups $G_{K_w}$ for $w\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ with $v(w) = v$. Since a global field has no non-trivial algebraic extension in which every prime splits completely, we get $H/N= G_{K_v}/H\cong G_{k(v)}$, thus $H=G_{K_v}$. Since $(K_w)'=K'_{w'}$, this shows that $(K_v)'$ is a henselization of $K'$ with respect to $v'=\sigma(v)$. We write $K'_{v'} = (K_v)'$.
